Title Goes Here \thanks{The research was supported by UBACyT20020170100428BA and the CLIMAX Project funded by Belmont Forum/ANR-15-JCL/-0002-01. Elio Campitelli was supported by a PhD grant from CONICET, Argentina.}

### 2021-04-09 analysis/paper/shceof.tex
Renderiza todo

\begin{figure*}
\includegraphics{../figures/psa-eof2-1} \caption{Relationship between the Real and Imaginary parts of cEOF2 and the PSA1 and PSA2 modes computed as the second and third EOFs of seasonal geopotential height anomalies \citep{mo2001}. For the period 1979 -- 2019.}\label{fig:psa-eof2}
\end{figure*}

The relationship between PSAs and the modes described from the cEOFs is also studied. Figure~\ref{fig:psa-eof2} shows the relationship between the two PSA indices and the Real and Imaginary phase of cEOF2. As anticipated by Figure~\ref{fig:eof2-regr-gh}, there is a strong correlation between PSA1 and Imaginary cEOF2 (Figure~\ref{fig:psa-eof2}b.1), and between PSA2 and Real cEOF2 (Figure~\ref{fig:psa-eof2}a.2). Conversely, there is no relationship between PSA1 and Real cEOF2, and between PSA2 and Imaginary cEOF2 (Figure~\ref{fig:psa-eof2} panels a.1 and b.2). So not only this cEOF2 represents well both the spatial structure and temporal evolution of the PSA modes, but it's also possible to make a rather clean association between its two phases and the two PSA modes.

>>>>

\caption{\label{tab:psa-eof2}Correlation between the Real and Imaginary parts of cEOF2 and the PSA1 and PSA2 modes computed as the second and third EOFs of seasonal geopotential height anomalies \citep{mo2001}. For the period 1979 -- 2019.}
\centering
\begin{tabular}[t]{l>{}l>{}l}
\toprule
\multicolumn{1}{c}{} & \multicolumn{2}{c}{cEOF2} \\
\cmidrule(l{3pt}r{3pt}){2-3}
PC & Real & Imaginary\\
\midrule
PSA1 & \cellcolor[HTML]{C3BBDE}{\textcolor{black}{-0.32 (CI: -0.57 -- -0.01)}} & \cellcolor[HTML]{6058A9}{\textcolor{white}{-0.83 (CI: -0.9 -- -0.69)}}\\
PSA2 & \cellcolor[HTML]{645BAB}{\textcolor{white}{-0.81 (CI: -0.9 -- -0.67)}} & \cellcolor[HTML]{F9F1F0}{\textcolor{black}{0.059 (CI: -0.25 -- 0.36)}}\\
\bottomrule
\end{tabular}
\end{table}

The relationship between PSAs and the modes described from the cEOFs is also studied. Figure~\ref{tab:psa-eof2} shows the relationship between the two PSA indices and the Real and Imaginary phase of cEOF2. As anticipated by Figure~\ref{fig:eof2-regr-gh}, there is a strong correlation between PSA1 and Imaginary cEOF2, and between PSA2 and Real cEOF2. Conversely, there is no relationship between PSA1 and Real cEOF2, and between PSA2 and Imaginary cEOF2. So not only this cEOF2 represents well both the spatial structure and temporal evolution of the PSA modes, but it's also possible to make a rather clean association between its two phases and the two PSA modes.
